---
title: "API Calls in R"
author: "Trevor French"
format: html
editor: visual
---

## Install Packages

``` r
install.packages(c('httr', 'jsonlite'))
```

## Require Packages

```{r}
library('httr')
library('jsonlite')
```

## Make Request

Pass a URL into the 'GET' function and store the response in a variable called 'res'.

```{r}
res = GET("https://api.helium.io/v1/stats")
print(res)
```

## Parse & Explore Data

Use the 'fromJSON' function from the 'jsonlite' package to parse the response data and then print out the names in the resulting data set.

```{r}
data = fromJSON(rawToChar(res$content))

names(data)
```

Go one level deeper into the data set and print out the names again.

```{r}
data = data$data

names(data)
```

Alternatively, you can loop through the names as follows.

```{r}
for (name in names(data)){print(name)}
```

Get the 'token_supply' field from the data.

```{r}
token_supply = data$token_supply

print(token_supply)
```

## Adding Parameters to Requests

Add 'min_time' and 'max_time' as parameters on a different endpoint and print the resulting 'fee' data.

```{r}
res = GET("https://api.helium.io/v1/dc_burns/sum",
    query = list(min_time = "2020-07-27T00:00:00Z"
                 , max_time = "2021-07-27T00:00:00Z"))

data = fromJSON(rawToChar(res$content))
fee = data$data$fee
print(fee)
```

## Adding Headers to Requests

Execute the same query as above except this time specify headers. This will likely be necessary when working with an API which requires an API Key.

```{r}
res = GET("https://api.helium.io/v1/dc_burns/sum",
    query = list(min_time = "2020-07-27T00:00:00Z"
                 , max_time = "2021-07-27T00:00:00Z"),
    add_headers(`Accept`='application/json', `Connection`='keep-live'))

data = fromJSON(rawToChar(res$content))
fee = data$data$fee
print(fee)
```
